### 2023-03-12 main/chapter_2ljets.tex
explain why offshell happened

>>>>

Our $\twoljets$ data selections are sub-optimal for targetting compressed
signal regimes because they require two hard leptons and only use two-lepton
triggers, while compressed signals tend to produce soft decay products and
can benefit from other $\met$ triggers for ISR scenarios.
Therefore, the goal of this off-shell study cannot be to contribute
competitive sensitivity.
It is also not an independent verification of the dedicated compressed
searches because our selections overlap.
Our meagre remaining goals are therefore to discover what sensitivity is
available in the $\twoljets$ data, and to provide a continuous extension of our
exclusion contours across the $\Delta m = m(Z)$ threshold
(as shown in the lower left of Figure~\ref{fig:2ljets_contours_c1n2}).
